### 2015-11-30 fundamentals/impl.tex
line 649 deleted unneccessary and somewhat untrue comment about regression tests
line 616: the authors did indeed mean git. We rearranged the sentence so that the word git does not appear near the word tool. this will avoid the concern that it might be a typo meaning toolkit. it will not fix the reviewers being English, however.

Automated version control, provided by the well-established \emph{distributed
  version control} tool git \cite{software_freedom_conservancy_git_2014}, is
at the heart of the QA strategy because it records the full history of any
change, along with metadata such as the author, a timestamp, and an
accompanying message. This makes it possible to identify when changes were
introduced, how they are related to other changes, and who made those changes.  If
necessary, it also facilitates reversing individual changes from a long and
intricate set of changes.  Version control also enables a code review process
descried in section \ref{sec:qa-review} below.

@@

Regression tests ensure significant unintended changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed.

>>>>

Automated version control, provided by git, a well-established \emph{distributed
  version control} tool \cite{software_freedom_conservancy_git_2014}, is
at the heart of the QA strategy because it records the full history of any
change, along with metadata such as the author, a timestamp, and an
accompanying message. This makes it possible to identify when changes were
introduced, how they are related to other changes, and who made those changes.  If
necessary, it also facilitates reversing individual changes from a long and
intricate set of changes.  Version control also enables a code review process
descried in section \ref{sec:qa-review} below.

@@

Regression tests ensure significant unintended changes do not
occur over the course of \Cyclus development.
Regression tests are implemented similarly to integration tests.
In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed.
